\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Add model approach.

\subsection{Zone-to-Zone Population Dynamics}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct),
will be hereafter referred to as zone-to-zone coverage.
\begin{description}
    \item[$\mathbf{A(t), B(t)}$] \hfill \\
    	Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$\mathbf{Z_{AB}(t)}$] \hfill \\
    	Zone-to-zone coverage of B from A
    \item[$\mathbf{v}$] \hfill \\
    	Required ambulance response time
    \item[$\mathbf{T_{AB}}$] \hfill \\
    	Travel time from A to B, given
    \item[$\mathbf{T_{BA}}$] \hfill \\
    	Travel time from B to A, given
    \item[$\mathbf{P_B}$] \hfill \\
    	Total population of B
    \item[$\mathbf{F_B(s)}$] \hfill \\
    	The probability curve for differences in travel time within B
   \item[$\mathbf{T_A}$] \hfill \\
    	Average travel time inside of A
    \item[$\mathbf{T_{A+}}$] \hfill \\
    	Average travel time in the direction of B to A inside of A
    \item[$\mathbf{T_{A-}}$] \hfill \\
    	Average travel time in the direction of A to B inside of A
   \item[$\mathbf{T_B}$] \hfill \\
    	Average travel time inside of B
    \item[$\mathbf{T_{B+}}$] \hfill \\
    	Average travel time in the direction of A to B inside of B
    \item[$\mathbf{T_{B-}}$] \hfill \\
    	Average travel time in the direction of B to A inside of B
    \item[$\mathbf{a, b}$] \hfill \\
    	Width of A and B respectively
    \item[$\mathbf{g}$] \hfill \\
    	Width of the gap between A and B
\end{description}

@@

The number of missed people is an important statistic that an Emergency Service Coordinator needs to have in
order to fully optimize their resources. In our system now, we predict this number with a certain level of accuracy,
but we are still prone to a relatively large amount of error. With a better understanding of the population and
geospacial makeup of each individual zone, we would be able to better optimize our resources and potentially save more people.

@@

\item Identify a set of nodes such that there is a large number of outgoing edges, thereby identifying potential
    split points, to divide each county into smaller subcounties. Make sure to account for overlap.

\item Allocate $n$ ambulances across the subcounties. If there are fewer ambulances than are necessary to cover
    the entire county, weight each subcounty by population size (save more people per ambulance).

\item Solve each subcounty for the optimal ambulance location, thereby finding a solution for the set as a whole.
\end{enumerate}

>>>>

Given that a county has $n$ zones, $k$ ambulances need to be placed to maximize the number of people who be reached in eight minutes or fewer. This system can be represented as a graph of $n$ and $k$ vertices. By analyzing all possible configurations, we can identify the ideal nodes to place the ambulances. This algorithm can be made more efficient---albeit less optimal---by employing a greedy heuristic that only focuses on the nodes that provide the most added coverage.

Each zone is a region, and therefore the population is not concentrated on one point. As a result, ambulances will often be able to cover only a fraction of a zone's total population. In order to find these fractions, we developed a model of population density for each zone by extrapolating from the provided average travel times between zones.

Travel time from a zone A to another zone B is not necessarily the same as the travel time in the opposite direction. This inconsistency could be due to a variety of factors, including differences in traffic, roads, and conditions. As a result, these two cases for each pair of zones must be handled separately.

\subsection{Zone-to-Zone Population Dynamics}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct),
will be hereafter referred to as zone-to-zone coverage.

A lack of spatial understanding of the county entails the use of a different type of population density. Rather than expressing population as a function of area or distance, we chose to express population density in terms of travel time from a reference point. This is analogous to plotting the number of people a vehicle is likely to meet at each time as it drives along a one-dimensional path.

The population that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be referred to as zone-to-zone coverage.

\begin{description}
    \item[$\mathbf{A(t), B(t)}$] \hfill \\
    	Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$\mathbf{Z_{AB}(t)}$] \hfill \\
    	Zone-to-zone coverage of B from A
    \item[$\mathbf{v}$] \hfill \\
    	Required ambulance response time
    \item[$\mathbf{T_{AB}}$] \hfill \\
    	Travel time from A to B, given
    \item[$\mathbf{T_{BA}}$] \hfill \\
    	Travel time from B to A, given
    \item[$\mathbf{P_B}$] \hfill \\
    	Total population of B
    \item[$\mathbf{F_B(s)}$] \hfill \\
    	The probability curve for differences in travel time within B
   \item[$\mathbf{T_A}$] \hfill \\
    	Average travel time inside of A
    \item[$\mathbf{T_{A+}}$] \hfill \\
    	Average travel time in the direction of B to A inside of A
    \item[$\mathbf{T_{A-}}$] \hfill \\
    	Average travel time in the direction of A to B inside of A
   \item[$\mathbf{T_B}$] \hfill \\
    	Average travel time inside of B
    \item[$\mathbf{T_{B+}}$] \hfill \\
    	Average travel time in the direction of A to B inside of B
    \item[$\mathbf{T_{B-}}$] \hfill \\
    	Average travel time in the direction of B to A inside of B
    \item[$\mathbf{a, b}$] \hfill \\
    	Width of A and B respectively
    \item[$\mathbf{g}$] \hfill \\
    	Width of the gap between A and B
\end{description}

@@

The number of missed people is an important statistic that an Emergency Service Coordinator needs to have in
order to fully optimize their resources. In our system now, we predict this number with a certain level of accuracy,
but we are still prone to a relatively large amount of error. With a better understanding of the population and
geospatial makeup of each individual zone, we would be able to better optimize our resources and potentially save more people.

@@

\item Identify a set of nodes such that there is a large number of outgoing edges, thereby identifying potential
    split points, to divide each county into smaller sub-counties. Make sure to account for overlap.

\item Allocate $n$ ambulances across the sub-counties. If there are fewer ambulances than are necessary to cover
    the entire county, weight each sub-county by population size (save more people per ambulance).

\item Solve each sub-county for the optimal ambulance location, thereby finding a solution for the set as a whole.
\end{enumerate}
